Weed and Corn segmentation through Convolutional Neuronal Networks

### 2017-06-02 PaperBCJ.tex
Fix Tables

\begin{table}[h!]
\centering
\begin{tabular}{||c c c c c||} 
 \hline
 Phase & Train & Validation & Test & Total \\ [0.5ex] 
 \hline\hline
 Maize & 7581 & 1895 & 787 & 9476 \\ 
 Weed & 2023 & 505 & 300 & 2528\\[1ex] 
 \hline
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:1}
\end{table}

@@

One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{Potena:Nardi}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following. 
\\
\begin{table}[h!]
\centering
\begin{tabular}{||c c c c c||} 
 \hline
 Parameters & LeNet & AlexNet & cNET & sNET \\ [0.5ex] 
 \hline\hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 4500 & 3000 \\ 
  Accuracy(\%) & 78.84 & 95.266 & 99.33 & 90.4 \\
  Loss(\%) & 44.8471 & 12.7256 & 5.86 & 781.3 \\ [1ex] 
 \hline
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:1}
\end{table}

>>>>

\begin{table}[h!]
\centering
\begin{tabular}{|c | c | c | c | c|} 
 \hline
 Phase & Train & Validation & Test & Total \\ [0.5ex] 
 \hline
 Maize & 7581 & 1895 & 787 & 9476 \\ 
 Weed & 2023 & 505 & 300 & 2528\\[1ex] 
 \hline 
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:1}
\end{table}

@@

One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{Potena:Nardi}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following. 
\\
\begin{table}[h!]
\centering
\begin{tabular}{|l c c c c|} 
 \hline
 Parameters & LeNet & AlexNet & cNET & sNET \\ [0.5ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 4500 & 3000 \\ 
  Accuracy(\%) & 78.84 & 95.266 & 99.33 & 90.4 \\
  Loss(\%) & 44.8471 & 12.7256 & 5.86 & 781.3 \\ [1ex] 
 \hline \\
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:1}
\end{table}
